---
title: "R Markdown Pre-Workshop Actions"
fontsize: 11pt
header-includes:
- \usepackage[type1]{plex-serif}
- \usepackage[sfdefault]{plex-sans}
- \usepackage{crimson}
- \usepackage[T1]{fontenc}
- \usepackage{calc}
- \usepackage{enumitem}
- \usepackage[onehalfspacing]{setspace}
- \usepackage{changepage}
- \usepackage{xcolor}
output:
  html_document:
    df_print: paged
    css: styles.css
subtitle: For the R Markdown workshop on March 9 hosted by GPAC
classoption: onecolumn,
urlcolor: blue
---
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.5pt}}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey Everyone,

In order to make this workshop run smoothly, I'm asking everyone to make sure they have these installed on the computers they intend to use for the workshop. In case you're wondering, all of this is free so you won't need to worry about paying anything. If you open this PDF on the computer you intend to use for the workshop, I've hyperlinked the download links in the text below so it's easier for you to get what you need. If you have any problems, let me know and I'll do my best to help before March 9th. 

# Step 1: Download R, Version 3.4.3

**Note:** When you click the link below, you'll be taken to a website

  * [Download link For Mac OS X](https://cran.rstudio.com/bin/macosx/R-3.4.3.pkg)
  * [Download link For Windows](https://cran.rstudio.com/bin/windows/base/R-3.4.3-win.exe)
  * [Download link For Other Platforms](https://cran.rstudio.com)

# Step 2: Download RStudio, Version 1.1.423

  * [Download link For Mac OS X 10.6+](https://download1.rstudio.org/RStudio-1.1.423.dmg)
  * [Download link For Windows Vista/7/8/10](https://download1.rstudio.org/RStudio-1.1.423.exe)
  * [Download link For Other Platforms](https://www.rstudio.com/products/rstudio/download/#download)
  
## Step 2a (Mac Users Only): Install XQuartz

  * [Download link for XQuartz](https://dl.bintray.com/xquartz/downloads/XQuartz-2.7.11.dmg)

# Step 3: Install the `rmarkdown` & `tinytex` Package

After you've doneTo do that, copy the following code

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
